Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-03-24 2_SSL_EES/article/article_supplementary.tex
updated references

\begin{table}[h!]
    \begin{tabularx}{\textwidth}{|l|X|}
    \hline
    \textbf{Provider of References} & \textbf{References} \\
    \hline
    Stiftung Warentest (Germany) & \cite{Warentest2008}\cite{Warentest2009_1}\cite{Warentest2009_2}\cite{Warentest2010_1}\cite{Warentest2010_2}\cite{Warentest2011}\cite{Warentest2012}\cite{Warentest2013}\cite{Warentest2014_1}\cite{Warentest2014_2}\cite{Warentest2015}\cite{Warentest2016_1}\cite{Warentest2016_2}\cite{Warentest2018} \\
    \hline
    Konsument (Austria) & \cite{Konsument2010} \\
    \hline
    Which (UK) & \cite{Which2020} \\
    \hline
    Industry Periodicals & \cite{PM2020} \\
    \hline
    Government Reports & \cite{council2013assessment} \\
    \hline
    \end{tabularx}
\end{table}

@@

\begin{table}[h!]
    \begin{tabularx}{\textwidth}{|l|X|}
    \hline
    \textbf{Type of Source} & \textbf{References} \\
    \hline
    Scientific Publications & \cite{plossl2010wafer}\cite{bierhuizen2007performance}\cite{gencc2019distributed}\cite{chong2014performance} \\
    \hline
    Patents & \href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJPH11168235A}{JPH11168235A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DDE19921987A1}{DE19921987A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJPH11340514A}{JPH11340514A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJP2001044498A}{JP2001044498A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2005045893A1}{US2005045893A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2002093023A1}{US2002093023A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2006273339A1}{US2006273339A1}  \\
    \hline
    Other Publications & \href{https://web.archive.org/web/20170801160530/https://www.energy.gov/sites/prod/files/2015/02/f19/craford_innovation_sanfrancisco2015.pdf}{2015 presentation (www.energy.gov)} \newline
\href{https://web.archive.org/web/20170715230721/https://www.energy.gov/sites/prod/files/2016/02/f29/sun_china_raleigh2016.pdf}{2016 presentation (www.energy.gov)} \newline
\href{http://web.archive.org/web/20160425025936/https://www.slideshare.net/Yole_Developpement/yole-led-packagingjanuary2013reportsample}{2013 presentation (www.slideshare.net)} \\
    \hline
    \end{tabularx}
\end{table}

>>>>

\begin{table}[h!]
    \begin{tabularx}{\textwidth}{|l|X|}
    \hline
    \textbf{Provider of References} & \textbf{References} \\
    \hline
    Stiftung Warentest (Germany) & \cite{Warentest2008}\cite{Warentest2009_1}\cite{Warentest2009_2}\cite{Warentest2010_1}\cite{Warentest2010_2}\cite{Warentest2011}\cite{Warentest2012}\cite{Warentest2013}\cite{Warentest2014_1}\cite{Warentest2014_2}\cite{Warentest2015}\cite{Warentest2016_1}\cite{Warentest2016_2}\cite{Warentest2018} \\
    \hline
    Konsument (Austria) & \cite{Konsument2010} \\
    \hline
    Which (UK) & \cite{Which2020} \\
    \hline
    Industry Periodical & \cite{PM2020} \\
    \hline
    Government Report & \cite{council2013assessment} \\
    \hline
    \end{tabularx}
\end{table}

@@

\begin{table}[h!]
    \begin{tabularx}{\textwidth}{|l|X|}
    \hline
    \textbf{Type of Source} & \textbf{References} \\
    \hline
    Scientific Publications & \cite{plossl2010wafer}\cite{bierhuizen2007performance}\cite{gencc2019distributed}\cite{chong2014performance} \\
    \hline
    Patents & \href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJPH11168235A}{JPH11168235A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DDE19921987A1}{DE19921987A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJPH11340514A}{JPH11340514A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJP2001044498A}{JP2001044498A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2005045893A1}{US2005045893A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2002093023A1}{US2002093023A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2006273339A1}{US2006273339A1}  \\
    \hline
    Other Publications & \cite{craford2015}\cite{sun2016}\cite{yole2013packaging} \\
    \hline
    \end{tabularx}
\end{table}
